```{r}
library(readr)
library(reshape2)
library(ggplot2)
library(dplyr)
library(plotly)
```
# RandCardDist <- as.data.frame(read.csv("C:/Users/jhaij/Desktop/RandCardDist.csv"))
# RandCardDist <- t(RandCardDist)
# RandCardDist <- melt(RandCardDist)
# RandCardDist <- RandCardDist[c("Var1", "value")]
# ggplot() + geom_density(RandCardDist,mapping = aes(x = value, colour = Var1)) + geom_hline(yintercept = (1/52), linetype = "dashed", colour = "black", size = 2)
# freq <- RandCardDist %>% group_by(value) %>% summarise(freq = n()) 
# ggplot(freq) + geom_bar(mapping = aes(x = value, y = freq))
```{r}
RandCardDist <- as.data.frame(read.csv("C:/Users/jhaij/Desktop/Python/Card Shuffle/orderedRandData.csv", header = FALSE))
buckets <- paste("buckets", c(1:52))
RandCardDist <- cbind(buckets = buckets, RandCardDist)
RandCardDistMelt <- melt(RandCardDist, id.vars = "buckets")
RandCardDistMelt <- RandCardDistMelt[c(1,3)]
densPlot <- ggplot(RandCardDistMelt) + geom_density(mapping = aes(x = value, colour = buckets)) + geom_hline(yintercept = (1/52), linetype = "dashed", colour = "black", size = 2)
buckDistPlot <- ggplot(RandCardDistMelt, aes(x = buckets, y = value)) + geom_boxplot(mapping = aes(colour = "red")) + geom_jitter(position = position_jitter(0.2))
```
could use plotly(a_ggplot) to get interactive plot

after, select a bucket and convert it to an array using buckN <- as.data.frame.array(). then run ks.test(buckN, "punif", 1,52)

ks.test:
```{r}
x <- RandCardDistMelt %>% dplyr::filter(buckets == "buckets 1")
x <- x[2] %>% as.matrix()
dd<-data.frame(x)
ks.test(x,"punif",1,52)

# ed <- ecdf(x)
# emp <- ed
# emp <- as.matrix(emp)
# maxdiffidx <- which.max(abs(emp-punif(dd$x,1,52)))
# maxdiffat <- dd$x[maxdiffidx]

p<-ggplot(aes(x),data=dd)+stat_ecdf()+theme_bw()+stat_function(fun=punif,args=list(1,52))
# p<-p+labs(title="ECDF and theoretical CDF")+geom_vline(x=maxdiffat, lty=2)
p
```

